\subsection{UI}\label{subsec:ui}
This directory is very extensive and every subdirectory contains other subdirectories.
Hence, this part describes only brief description.


\textbf{Aircrafts} directory consists of \textbf{Aircrafts} screen and \textbf{Aircraft Detail} screen.
In addition, there is placed \textbf{Aircraft Operation Bloc} and \textbf{Aircraft Form Bloc} for serving data in a form.


\textbf{Common} directory consists of shareable elements in user interface.
For example, they are dialogs, tile dividers, navigation bars and progress indicators.


\textbf{Dashboard} directory consists of \textbf{Location Bloc}, \textbf{Map Bloc} and the nested \textbf{Blocs} described in the Software architecture section~\ref{subsec:bloc-and-hydrated-bloc}.
In addition, it contains all graphic elements that you can see in Dashboard screen including Search screen with the managing Blocs.
Dashboard is the most complex part of this application.
It assamblies data about zones, drones and places and placing them into the map.


\textbf{Devices} directory consists of \textbf{Devices} screen and \textbf{Device Detail} screen.
In addition, there is placed \textbf{Device Operation Bloc}, \textbf{Device Detail Bloc} for control the switching elements in Device Detail Screen and \textbf{Device Form Bloc} for serving data in a form.


\textbf{Flights} directory consists of\textbf{Flights} screen, \textbf{Flight Detail} screen, \textbf{In-flight} screen and \textbf{Plan a flight} screens.
In addition, there is placed \textbf{Flight Operation Bloc} and \textbf{Flight Form Bloc} for serving data in a form.


\textbf{Intro} directory consists of \textbf{Login} and \textbf{Registration} subdirectories.
Both of them contains UI components and its own logic.
It is arranged to self-organized directories because encapsulation.


\textbf{Profile} directory consists of \textbf{Profile} screen and \textbf{Profile Detail} screen.
In addition, there is placed \textbf{Profile User Bloc} and \textbf{Profile Detail Form Bloc} for serving data in a form.

