% arara: pdflatex
% arara: bibtex
% arara: pdflatex
% arara: pdflatex


% options:
% thesis=B bachelor's thesis
% thesis=M master's thesis
% czech thesis in Czech language
% english thesis in English language
% hidelinks remove colour boxes around hyperlinks

\documentclass[thesis=M,english]{template/FITthesis}[2019/12/23]

\usepackage[utf8]{inputenc} % LaTeX source encoded as UTF-8
% \usepackage[latin2]{inputenc} % LaTeX source encoded as ISO-8859-2
% \usepackage[cp1250]{inputenc} % LaTeX source encoded as Windows-1250

% \usepackage{subfig} %subfigures
% \usepackage{amsmath} %advanced maths
% \usepackage{amssymb} %additional math symbols

\usepackage{graphicx}
\usepackage{dirtree} %directory tree visualisation
\usepackage{pdfpages}
\usepackage{import}
% \usepackage{xevlna}

% % list of acronyms
% \usepackage[acronym,nonumberlist,toc,numberedsection=autolabel]{glossaries}
% \iflanguage{czech}{\renewcommand*{\acronymname}{Seznam pou{\v z}it{\' y}ch zkratek}}{}
% \makeglossaries

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % 
% EDIT THIS
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % 

\department{Department of Software Engineering}
\title{Cross-platform mobile application for safer drone operations}
\authorGN{Jan} %author's given name/names
\authorFN{Mat{\v e}jka} %author's surname
\author{Jan Mat{\v e}jka} %author's name without academic degrees
\authorWithDegrees{Bc. Jan Mat{\v e}jka} %author's name with academic degrees
\supervisor{Ing. Luk{\' a}{\v s} Brchl}
\acknowledgements{I would like to thank my family, my girlfriend and friends for support while writing this thesis and all my studies.
I also would like to thank my supervisor Ing. Luk{\' a}{\v s} Brchl, for this chance to realize me in mobile application development.}

%----------------------------------------------------------------------------------------------------------------------------------------

\abstractEN{This master's thesis focuses on cross-platform mobile application development in the Flutter framework for safer drone operations.
This thesis contains full application analysis, design, and implementation. Its main functionality is the management of drones and identification devices attached to drones, showing restricted flight zones, and planning and watching drone flights.

The analysis emphasizes the analysis of the existing web platform and all infrastructure, which provides data to the client and third-party applications.
The design contains a description of the application structure and used architecture patterns of the Flutter framework.
The implementation describes details about realization and contains detailed instructions to launch in the development, test, and production environment.
Concurrently, it contains a description of the necessary configuration files that differs across the various environment and have security disposition.}

%----------------------------------------------------------------------------------------------------------------------------------------

\abstractCS{Tato diplomov{\' a} pr{\' a}ce se zab{\' y}v{\' a} v{\' y}vojem multiplatformn{\' i} mobiln{\' i} aplikace ve frameworku Flutter pro bezpe{\v c}n{\v e}j{\v s}{\' i} provoz dron{\r u}.
Pr{\' a}ce obsahuje kompletn{\' i} anal{\' y}zu, n{\' a}vrh a samotnou implementaci aplikace, jej{\' i}{\v z} hlavn{\' i} fukcionalitou je spr{\' a}va dron{\r u} a identifika{\v c}n{\' i}ch za{\v r}{\' i}zen{\' i} p{\v r}ipevn{\v e}n{\' y}ch k dron{\r u}m, zobrazov{\' a}n{\' i} zak{\' a}zan{\' y}ch z{\' o}n pro lety a pl{\' a}nov{\' a}n{\' i} a sledov{\' a}n{\' i} let{\r u} dron{\r u}.

V anal{\' y}ze je kladen d{\r u}raz na rozbor existuj{\' i}c{\' i} webov{\' e} platformy a cel{\' e} infrastruktury, kter{\' a} poskytuje data klientsk{\' y}m aplikac{\' i}m a aplikac{\' i}m t{\v r}et{\' i}ch stran.
N{\' a}vrh obsahuje popis struktury aplikace a pou{\v z}it{\' e} architektonick{\' e} vzory frameworku Flutter.
Implementace popisuje detaily o realizaci a obsahuje podrobn{\' y} n{\' a}vod pro spu{\v s}t{\v e}n{\' i} ve v{\' y}vojov{\' e}m, testovac{\' i}m a produk{\v c}n{\' i}m prost{\v r}ed{\' i}.
Z{\' a}rove{\v n} obsahuje popis d{\r u}le{\v z}it{\' y}ch konfigura{\v c}n{\' i}ch soubor{\r u}, kter{\' e} se li{\v s}{\' i} nap{\v r}{\' i}{\v c} r{\r u}zn{\' y}mi prost{\v r}ed{\' i}mi a maj{\' i} bezpe{\v c}nostn{\' i} charakter.}

%----------------------------------------------------------------------------------------------------------------------------------------

\placeForDeclarationOfAuthenticity{Prague}
\keywordsCS{Multiplatformn{\' i}, mobiln{\' i}, aplikace, dron, {\v r}{\' i}zen{\' i}, Flutter.}
\keywordsEN{Cross-platform, mobile, application, drone, operation, Flutter.}
\declarationOfAuthenticityOption{1} %select as appropriate, according to the desired license (integer 1-6)
% \website{http://site.example/thesis} %optional thesis URL


\begin{document}

% \newacronym{CVUT}{{\v C}VUT}{{\v C}esk{\' e} vysok{\' e} u{\v c}en{\' i} technick{\' e} v Praze}
% \newacronym{FIT}{FIT}{Fakulta informa{\v c}n{\' i}ch technologi{\' i}}


\input{chapters/main_chapters}


\bibliographystyle{template/iso690}
\bibliography{mybibliographyfile}

\setsecnumdepth{all}
\appendix

\input{chapters/formal/acronyms}

\input{chapters/formal/sd_card_content}

\end{document}


