\subsection{JsonSerializable}\label{subsec:jsonserializable-classes}
Json Serializable interface offers generating methods for serialization and deserialization classes.
Json Annotation annotates these classes.
These classes are converted, and the process creates the methods via the build runner library.
The advantage is that developers have not to code these methods by hand.
They can re-generated every time it is needed to change the class structure.

\textbf{Request classes} are used for store and serialization of data before the Rest client will send it.
This directory contains only Login Request and Register Request classes.

\textbf{Response classes} are used for store and deserialization of data after the Rest client has received it.
This directory contains:
\begin{itemize}
    \item \textbf{Aircraft Detail Response} -- is used for passing aircraft data in Aircraft Repository,
    \item \textbf{Aircraft Overview Response} -- is used for a nested object in Flight Info Response in Flight Repository,
    \item \textbf{Api Error} -- is used for processing of \acrshort{api} error message in each of Repositories,
    \item \textbf{Device Detail Response} -- is used for passing device data in Device Repository,
    \item \textbf{Device Live Response} -- is used for passing device live data in Device Repository,
    \item \textbf{Device Telemetry Response} -- is used for passing device telemetry live data in Device Repository,
    \item \textbf{Dronetag Overview Response} -- is used for a nested object in Flight Info Response in Flight Repository,
    \item \textbf{Flight Info Response} -- is used for passing flight data in Flight Repository,
    \item \textbf{Flight Statistics Response} -- is used for flight statistics data in Flight Repository,
    \item \textbf{Location} -- is used for passing latitude and longitude data in almost each of Repositories,
    \item \textbf{Region Response} -- is used for a nested object in Zone Response and Flight Info Response,
    \item \textbf{Take Off Response} -- is used for a nested object in Flight Info Response in Flight Repository,
    \item \textbf{Telemetry Response} -- is used for passing telemetry data in Device Repository,
    \item \textbf{User Profile Response} -- is used for passing user data in User Repository,
    \item \textbf{Zone Response} -- is used for passing zone data in Zone Repository.
\end{itemize}
