\section{Software Architecture}\label{sec:software-architecture}
This section focuses on the architecture of this application implementation.
Because the definition of software architecture has been already clarified, it will be emphasized to certain components that were used in the implementation.

In software architecture, there has been verified a pattern of using libraries that offers using of generic classes.
These classes include already implemented logic that is based on standards, and thus it helps to simplify development and maintain code more readable.
For better understanding, Bloc and Hydrated Bloc classes will be described in the section~\ref{subsec:bloc-and-hydrated-bloc} of this chapter.
\newpage
There would be useful to discuss the difference between common Bloc and its extended class Hydrated Bloc.
Both of them use the sink and stream concept that works on the stream subscription principle.
The Hydrated Bloc offers persistent storage storing and loading with \textbf{fromJson} and \textbf{toJson} methods.
It helps to have an application working more smoothly due to storing of data in the phone.
Only continuous loading data via the network whenever a user needs them has significant impact to the response time in the application.


\input{chapters/main_content/software_architecture_and_design/software_architecture/dependencies}

\input{chapters/main_content/software_architecture_and_design/software_architecture/bloc_and_hydrated_bloc}

\input{chapters/main_content/software_architecture_and_design/software_architecture/json_serializable}

\input{chapters/main_content/software_architecture_and_design/software_architecture/dio_class}
