\chapter{Software design}\label{ch:software-design}
Describe software design

%-------------------------------------------------
\section{Common}\label{sec:common}
describe content
todo

%-------------------------------------------------
\section{IO}\label{sec:io}
todo

\subsection{Model}\label{subsec:model}
Model~directory~contains objects that~are produced by~API endpoint of~Dronetag backend.
It is divided to \textbf{request} and \textbf{response} classes.

\subsection{Repositories}\label{subsec:respositories}
todo

\subsection{Services}\label{subsec:services}
todo

%-------------------------------------------------
\section{UI}\label{sec:ui}

\subsection{Aircrafts}\label{subsec:aircrafts}
todo

\subsection{Common}\label{subsec:common}
todo

\subsection{Dashboard}\label{subsec:dashboard}
todo

\subsection{Devices}\label{subsec:devices}
todo

\subsection{Flights}\label{subsec:flights}
todo

\subsection{Intro}\label{subsec:intro}
In additional, the Introduction directory consists of \textbf{Login} and \textbf{Registration}.
Both of them contains UI components and its logic.
It is arranged to self-organized directories.

\subsection{Profile}\label{subsec:profile}
todo

%-------------------------------------------------
\section{Util}\label{sec:util}
todo

\subsection{Error}\label{subsec:error}
todo

\subsection{Extensions}\label{subsec:extensions}
The Extensions directory contains:
\begin{itemize}
    \item Polygon Extension,
    \item Circle Extension,
    \item Number Extension and
    \item String Extension.
\end{itemize}
\textbf{Polygon Extension} offers to find out if a \textbf{Point}\cite{} consisted of latitude and longitude is lying in the given \textbf{Polygon}\cite{}.
It is based on the mathematical problem when we looking for the result if a y-axis of a point goes through an even number of border lines of the given polygon.
To solve how find out if the y-axis goes through is based on the problem which deals with two lines go through each other.
All the problem is described in this paper\cite{}.
% \cite{}: http://www.dcs.gla.ac.uk/~pat/52233/slides/Geometry1x1.pdf

\textbf{Circle Extension} offers to find out if a \textbf{Point}\cite{} consisted of latitude and longitude is lying in the given \textbf{Circle}\cite{}.
It is based on the \textbf{Pythagorian theorem} that solves a computation of the longest line in a .

\textbf{String Extension}
\textbf{Number Extension}
Only notes:
A component with interesting logic could be the Polygon Extension.
It is for finding out if a given point lies in the Polygon.

todo
And computation of distance and transform it on lat long coordinates !

\subsection{Preferences}\label{subsec:preferences}
todo
