\chapter{User interface design}\label{ch:user-interface-design}

Describe a difference between Lo-Fi and Hi-Fi prototype.

I did not a Lo-Fi prototype because Dronetag is Start-up, company with limit budget, so I focused only on the Hi-Fi.
When I was making Hi-Fi, I inspired by a few concurrency application, which shows permitted flight zones and danger areas.

Describe a difference between UI and UX.
Write about techniques and reasons to concentrate on this things.

\section{Hi-Fi prototype}\label{sec:hi-fi-prototype}
We made a Hi-Fi prototype in Adobe XD.
We focused to the simplicity and "briefness" and keep focus on the most important rules of design UI and UX.
These rules are:
\begin{itemize}
    \item
\end{itemize}

\subsection{Dashboard}\label{subsec:dashboard2}
This screen contains:
\begin{itemize}
    \item Map canvas,
    \item Search button,
    \item Profile button that represents Menu,
    \item My location button,
    \item Map layer button and
    \item Fly now button.
\end{itemize}
In addition, for a logged user it contains:
\begin{itemize}
    \item Device status (if the user has already added some),
\end{itemize}

\subsection{Intro screen}\label{subsec:intro-screen}

\subsection{Login screen}\label{subsec:login-screen}

\section{Usability testing}\label{sec:usability-testing}
Describe usability testing flow

Describe right zoom when a user chooses drone on Dashboard map...

\subsection{Results}\label{subsec:results}

\subsection{Main mistakes in UI design}\label{subsec:main-mistakes-in-ui-design}