\section{Altitude Angel}\label{sec:altitude-angel}
Altitude Angel ecosystem can be divided into these three subsystems:
\begin{itemize}
    \item Guardian UTM,
    \item Guardian Mobile,
    \item Drone Safety Map.
\end{itemize}

\subsection{GuardianUTM}\label{subsec:guardianutm}
"GuardianUTM provides software developers and drone manufacturers with the tools and data to access accurate, up-to-date and relevant aeronautical, environmental, regulatory and drone-centric operational data."~\cite{altitudeAngel}
This system ensures the integration of flight aviation data in the airspace.


\subsection{Drone Safety Map}\label{subsec:drone-safety-map}
It is a mobile and web application for drone pilots connected to GuardianUTM.
Its goal is to show zones and flight missions of all pilots.
\newline
\newline
Advantages:
\begin{itemize}
    \item The application shows flight zones in all countries.
    \item Aside from zones, it also shows hazardous objects like high-voltage wires, schools, police officers, and gas stations.
    There is much information and map data is not clear.
    \item It supports CAA UK (Civil Aviation Authority of the United Kingdom) that integrates its solution into the application of NATS Drone Assist.~\cite{droneAssist}
    It is a drone safety application from the NATS (National Air Traffic Services).
\end{itemize}
Disadvantages:
\begin{itemize}
    \item The registration is inconvenient with an additional password setting via e-mail.
    \item The flight plan history contains unnecessary text fields (flight title, description, and timezone).
    The flight plan history does not exist.
    \item There is no chance to share telemetries in real-time (for example, connection with DJI drones).
    \item It does not allow the planning of more complex zones than circles.
    \item It is difficult to determine a reserved zone for flight against restricted zone by the authorities in the user interface.
    \item Completely, the mobile and web application has less elaborate user interface beside AirMap.
    For example, it shows terms \& conditions before every flight.
    \item The mobile application contains bugs in the mission planning and searching.
\end{itemize}
