\section{MAIA}\label{sec:maia}
MAIA is an application by the UpVision company that is primarily used for displaying understandable information about flight zones.~\cite{maia}

The user interface is mostly consisted of the map that contains national flight zones and restrictions.
In case of sufficient data, it will display the location of real-time drones on the map and their details about aircrafts in the airspace.

The signed up users can have a summary of his drones, battery status and flight history.
Every user can contact any pilots via the Messenger function, that are visible on the map.

A user can add an insurance confirmation, pilot certification and permission for flight operations in the application.
Besides, users can share their favorite flight locations.

The application of the enterprise version promises functions for drone fleet owners such as geofencing, central management, drone detection and collision detection.
\newline
\newline
Advantages:
\begin{itemize}
    \item The application shows positions of drones in real-time.
    \item The application shows national flight zones and restrictions.
    \item The application provides data about flight zones in the Czech Republic and other countries.
\end{itemize}
Disadvantages:
\begin{itemize}
    \item The web platform has just few functions.
    Users can be signed in, but it contains no map layers.
    \item The application requires the MAIA tracker.
    Otherwise, it does not support another function.~\cite{maia}
    \item The mobile application contains many bugs and is not up-to-date.
\end{itemize}