\chapter{Software architecture and design}\label{ch:software-architecture-and-design}
This chapter describes the software architecture and design of the mobile application.
In the beginning, let us clarify the difference between software architecture and design.

In Software development, Software architecture means the design of application from a higher perspective than Software design.
In opposite, Software design means the division of the code into parts that describe implementation details accurately.
It means that when anyone starts with a new application project, it is essential to arrange the project into small alone parts.
These parts should meet the encapsulation and comprehensive rule.

Libraries offering generics classes that include already implemented logic help to simplify and do code more readable thanks to the standards.
For better understanding, we will describe it in the following example.

Architecture usually means a division into more significant self-driven parts.
Typically, there are concepts like MVC (Model-View-Controller) or their extended descendants like MVP (Model-View-Presenter) or MVVM (Model- View-ViewModel).
The newer great concept in Flutter is Bloc.
We have already explained what the Bloc is in the Flutter Analysis Flutter Analysis chapter~\ref{ch:flutter-analysis}, so we will not clarify it anymore.

\input{chapters/main_content/software_architecture_and_design/software_architecture/software_architecture}

\input{chapters/main_content/software_architecture_and_design/software_design/software_design}