\setsecnumdepth{part}
\chapter{Introduction}\label{ch:introduction}
This thesis focuses on safer drone operation.%zajištění bezpečnosti provozu dronů.
In 2012, drones began to spread in the Czech Republic.
In that time, they were toys that were built by hobby pilots' hands at home.%V té době to byly spíše hračky, které si hobby piloti sestavovali sami doma.
Thus, there were technical problems with them.%Proto je provázeli obvykle technické problémy.

After a while, the big companies began to see a possible potential and then have started to build their future vision.%Po určité době v nich začali vidět potenciál velké firmy a začali na nich stavět svou vizi budoucnosti.
For example, Amazon company introduced its concept of autonomous drone able to delivery goods from logistic warehouses directly to customers' homes.%Například společnost Amazon představila svůj koncept autonomních dronů schopných doručovat zboží z logistických skladů přímo k zákazníkům domů.
This news was published in Forbes magazine by Jillian D'Onfro.\cite{amazonArticle}
The customer could be more satisfied with this shopping because the time of delivering can be cut on as the tiny part of the time as now.
Even Amazon has decided to produce their own drone products.
One of them is Prime Air delivery drone.

To make the delivery process easier, Amazon is developing autonomous drones application to minimize costs.
Hence, we can expect a significant expansion of autonomous aircrafts.
Potentially, it could be possible to use drones to delivery the medical materials in case of big accident.
Especially, after a hurricane, fight conflict, or even during epidemic diseases like Coronavirus this time.

With increasing number of drone owners has started to arise problems. %Zvýšením počtů majitelů dronů začali vznikat problémy.
Most of the hobby pilots broke the law and endangered the aviation safety when they were flying. %Většina hobby pilotů při létech porušovala zákon a ohrožovala bezpečnost leteckého provozu.
The reason was an ignorance of laws that were needed to know for crew flight pilots until that time. %Důvodem byla neznalost patřičných zákonů, které do té doby museli znát pouze piloty posádkových letounů.
Hence, it has started to solve this problem. %Proto se postupem času začal tento problém řešit.
Although, the laws for crew flight pilots is partly related to the drone pilot, too. %Přestože se na piloty bezpilotních letounů částečně vztahují i ty posádkových letounů.
On the other hand, the drone pilots just know the symbols and restricted areas and do not have to be concentrated on full course of instruction like crew flight pilots.
%Na druhou stranu, pilotům dronů stačí znát značení zón  a nemusí být zatížení kompletní instruktáží jako jsou piloti posádkových letounů.

It is needed to know the basic type and description of zones for safer operation. %Pro bezpečný provoz je nutné znát základní typy a značení zón.
These zones separates into many types. %Tyto zóny se dělí na několik typů.
They are FIS (Flight Information Region), CTR (Control Zone), TMA (Terminal Maneuvering Area), ATZ (Aerodrome Traffic Zone), airports, P (Prohibited Area), R (Restricted Area), D (Dangerous Area), TRA (Temporary Reserved Area) and TSA (Temporary Segregated Area).\cite{airspace}

In addition, there are important parameters by the zones.
Lower and upper altitude level.
These flight levels divides into some groups by the altitude given in feet units. %Tyto hladiny (levels) se dělí do několika skupin podle altitude uváděných v feet units.
Further, it is needed to realize that the given altitude can be one of two types. %Dále je nutné si uvědomit, že uvedená výška může být dvojího typu.
AMSL (Above Mean Sea Level) nad AGL (Above Ground Level).
It means we have to beware the type of given altitudes and in case of AMSL we have to realize what our current altitude is to avoid restricted areas.
%To znamená, že si musíte na tyto jednotky dát pozor a a v případě AMSL si uvědomit v jaké aktuální výšce se nacházíte, aby jste při letu nevletěli do zakázané zóny.

In addition, the airspace divides into A-G classes.\cite{airspace} %Dále se vzdušný prostor dělí na třídy A-G.
There is an obligation to announce a flight for the A-E classes to authorities and Navigation Service of the Czech Republic approves the flight. %Pro třídy A-E platí nutnost svůj let hlásit a Air Navigation Service of the Czech Republic letům přiřazuje povolení.
The F and G classes are lower flight levels, so it is not needed to request an authorization on Air Navigation Service of the Czech Republic. %Třídy F a G jsou v nižšší letové hladině a není v nich nutné žádat o povolení Air Navigation Service of the Czech Republic.

Air Navigation Service of the Czech Republic released a website L{\' e}tejte zodpov{\v e}dn{\v e} (Fly carefully) about Drones problematics and wrote advisories for the hobby drone pilots in understandable way.
This website is closely described in Related projects chapter~\ref{sec:fly-carefully}.


\section{Motivation}\label{sec:motivation}
There was a motivation to participate on this thesis because I wanted to realize myself in the mobile application development. %Motivací podílet se na této práci pro mě byla v tom, že se mohu realizovat ve vývoji mobilních applikací.
The reason was, that I am interested in to try something new, and I have been only experiences of the web development so far. %Důvodem byl můj zájem si vyzkoušet něco nového, jelikož mám zatím pouze zkušenosti z webového vývoje.
The other reason was the successes in various competitions of both of the Dronetag company co-founders Luk{\' a}{\v s} Brchl and Marian Hlav{\' a}{\v c}. %Dalším důvodem byly úspěchy v soutěží dvou zakládajících členů společnosti Dronetag
They won a hackathon, and even they were prized in the competitions on the European and world level. % ale dokonce se umístili v soutěžích na evropské a světové úrovni
There were another motivation to participate on a product with huge potential and we can call it product of the future. %Motivací pro mě bylo také možnost podílet se na produktu, který má velký potenciál a můžeme ho nazvat produktem budoucnosti.
There is a reason why the business with drones is called exponential.


\section{Objectives}\label{sec:objectives}
The goal of this thesis is to develop a cross-platform mobile application for safer drone operation.
The application will be implemented by the best-practice principles in the Flutter framework.
Concurrently, this thesis contains a description fo the basic Flutter framework concepts in Flutter Analysis chapter.
The implementation contains partly testing by unit tests and deployment specification, too.
The application will meet all functional requirements. %Aplikace bude splňovat všechny funkční požadavky.
These requirements are drawing of flight zones in the map, showing real time data about flying drones attached a Dronetag device, flight planning and management of my aircrafts, devices and flight history.
%vykreslování zón v mapě, zobrazování létajících dronů opatřených Dronetag zařízením v reálném čase, plánování letů a management vlastních letounů, zařízení a historie letů.
