\chapter{User Interface Design}\label{ch:user-interface-design}
This chapter is focused on the user interface design of the Dronetag mobile application.
It starts with an explanation of difference between \acrshort{ui}~(\acrlong{ui}) and \acrshort{ux}~(\acrlong{ux}), and continues with a description about the user interface structure of the application.
So, it contains a list of screens that are shown to users when they go through the application.

The main difference between \acrshort{ui} and \acrshort{ux} is in the approach.
\acrshort{ui} approach emphasizes a combination of visual elements such that the final concept of visualization fits together.
\acrshort{ux} approach emphasizes an arrangement of these visual elements such that their arrangement was logical, and it was close to human thinking.~\cite{prototyping}
There are many visual elements that can interact with users.
They can be:
\begin{itemize}
    \item A text label,
    \item A text field,
    \item A button,
    \item A checkbox,
    \item A List view,
    \item A menu,
    \item An icon,
    \item An image,
    \item And others.
\end{itemize}
\acrshort{ui} approach deals with their skin~-~for example, a color, size, shadow, border, shape, and others.
\acrshort{ux} approach focuses on the size and position on the screen.
The arrangement of elements in screens should be comprehensive and should make sense to users.

The user interface design phase usually includes \acrshort{lofi}~(\acrlong{lofi}) and \acrshort{hifi}~(\acrlong{hifi}) prototyping.~\cite{effectivePrototyping}
\acrshort{lofi}, how the name hints, is a simplified sketch without colors with a purpose to incorporate the elements on a screen together.
It is cheaper than \acrshort{hifi} and takes only a few hours to finish.
The benefits are:
\begin{itemize}
    \item Focus on design and concepts,
    \item Focus on design and concepts,
    \item Accessible to everyone.~\cite{hiFiLoFiPrototypeArticle}
\end{itemize}
In opposite, \acrshort{hifi}, how the name hints, includes a fidelity design that should correspond to the final product.
It is more expensive than \acrshort{lofi} and usually takes a few days.
The benefits are:
\begin{itemize}
    \item More familiar to users,
    \item Pinpoint specific components to test,
    \item More presentable to stakeholders.~\cite{hiFiLoFiPrototypeArticle}
\end{itemize}
To more information about fidelity, anyone can read this article~\cite{hiFiLoFiPrototypeArticle}.

\acrshort{lofi} prototype has not been created because Dronetag is Start-up, a company with a limited budget, so there is only the \acrshort{hifi} prototype.
When \acrshort{hifi} was being made, it was inspired by a few competitor applications, which show permitted flight zones and danger areas.
These applications are described in the Related projects chapter~\ref{ch:related-projects}, so they will not be discussed anymore.


\input{chapters/main_content/user_interface_design/hifi_prototype/hifi_prototype}

\input{chapters/main_content/user_interface_design/usability_testing/usability_testing}
